---
title: "Lab2-R"
author: "Clayton Glenn"
date: "January 22, 2018"
output:
  word_document:
    toc: yes
  html_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 5
    number_sections: yes
    toc: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# TASKS

## Task 1

### Show Working Directory
```{r}
getwd()
```



## Task 2

### Read Data File
```{r read data}
mpg.df=read.table("EPAGAS.csv",header=TRUE,sep=",")
head(mpg.df)
```



## Task 3

### Create Z vector from MPG
```{r z vector}
mpg=mpg.df$MPG
z=scale(mpg)
class(z)
```

### Verify Z-BAR and S^2vZ
```{r Z-Bar and S2}
apply(z,2,mean)
apply(z,2,sd)
```

### Find the values of mpg that are possible outliers
```{r Possible Outliers}
mpg[abs(z)>=2 & abs(z)<=3]
```

### Find the values of mpg that defined as outliers
```{r Outliers}
mpg[abs(z)>3]
```

### Lattice Dotplot with outliers and possible outliers 

```{r MPG DotPlot}
mycol = ifelse(abs(z)>3, "Red",
        ifelse(abs(z)>=2 &abs(z)<=3,"Blue", "Black"))  
library(lattice)
dotplot(mpg,col=mycol)
```



## Task 4

### Boxplot of MPG
```{r MPG BoxPlot}
boxplot(mpg, data=mpg, notch=TRUE, col=(c("green3")), main="Miles Per Gallon", horizontal = TRUE)
```

### Exact Proportion Within 2 STD's of the Mean.

```{r Actual Proportion}
sprintf("%.0f%%", length(mpg[abs(z)<2])/length(mpg) * 100)
```

### Chebyshev's Theorum

(1 - 1/(#)^2) of the Data lies within 2 STD's

```{r Chebyshevs Theorum}
sprintf("%.0f%%", (1 - 1/2^2)*100)
```

According to the theorum, ATLEAST 75% of the data lies within 2 STD's. In this case 96% of the lies within 2 STD's, so Chevyshev's theorum is correct and does agree with the data.

### Empirical Rule

Approximately 95% of Data lies within 2 STD's of the Mean
```{r Empirical Rule}
sprintf("%.0f%%", 95)
```

The Empirical Rule responds very well to the data, due to the fact that the rule states that APPROXIMATELY 95% of the data lies within 2 STD's and according to the actual proportion of data, which is 96%, the Eprical Rule is a very close estimate to the real proportion.
