---
title: "Lab14"
author: "Clayton Glenn"
date: "April 28, 2018"
output:
  html_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 5
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Task1

##Get Working Directory

```{r}
getwd()
```



#Task2

##Least Squares Function

```{r}
mylsq=function(x,y){
  ssxx=sum((x-mean(x))^2 )
  ssxy=sum((x-mean(x))*(y-mean(y)))
  b1hat=ssxy/ssxx
  b0hat=mean(y)-b1hat*mean(x)
    return(list(b0hat=b0hat,b1hat=b1hat))
}
```

##Random Sample with Least Squares Line Applied

```{r}
x=1:20
set.seed(29);y=4+6*x + rnorm(20,0,5)
line = mylsq(x=x,y=y)
plot(y~x, pch = 16, xlab = "X-Values", ylab = "Y-Values", main = "Random Sample")
abline(line$b0hat, line$b1hat, lwd = 2, col = "Blue")
```

###Calculations

Intercept of the Least Squares Line
```{r}
line$b0hat
```

Slope of the Least Squares Line
```{r}
line$b1hat
```

###Calculation Check

```{r}
slr=lm(y~x); summary(slr)$coefficients
```
According to the summary, the coefficients match the coefficients we calculated.



#Task3

##Predictions of Sample

```{r}
mypred = function(x, b0hat, b1hat){
  y=b0hat+b1hat*x
  y
}
plot(y~x, pch = 16, xlab = "X-Values", ylab = "Y-Values", main = "Random Sample")
abline(line$b0hat, line$b1hat, lwd = 2, col = "Blue")
points(x=15.5,y=mypred(15.5, line$b0hat, line$b1hat), cex=3 ,col="Green",pch=19)
```
The predicted Y-Value for the X-Value of 15.5 is 98.12864.

##Orange Juice

###OJ Plot with Least Squares Line

```{r}
oj = read.csv("OJUICE.csv")
line = mylsq(x = oj$Pectin, y = oj$SweetIndex)
plot(oj$SweetIndex~oj$Pectin, pch = 16, ylab = "Sweetness Index", xlab = "Pectin", main = "OJ")
abline(line$b0hat, line$b1hat, lwd = 2, col = "Blue")
```

###$\hat \beta_0$ and $\hat \beta_1$

```{r}
line$b0hat
```
The predicted value of Pectin as zero of the OJ data is 6.252068 on the Sweetness Index.

```{r}
line$b1hat
```
The predicted slope of Sweetness to Pectin is -0.002310626.

###X as $\hat y_i = 300$

```{r}
mypred(300, line$b0hat, line$b1hat)
```
According to the least squares line, if pectin is 300, then the Sweetness Index of the orange juice is 5.55888.

##Drilling in Rock

###Plot of DrillRock with Least Squares Line

```{r}
rock = read.csv("DRILLROCK.csv")
line = mylsq(x = rock$DEPTH, y = rock$TIME)
plot(rock$TIME~rock$DEPTH, pch = 16, ylab = "Time", xlab = "Depth", main = "Drilling rock")
abline(line$b0hat, line$b1hat, lwd = 2, col = "Blue")
```

###$\hat \beta_0$ and $\hat \beta_1$

```{r}
line$b0hat
```
As Depth is zero, the predicted value of time to drill 5 feet is 4.789603.

```{r}
line$b1hat
```
The Time/Depth slope is 0.01438785.


#Task4

##Variance Function

```{r}
mysq=function(x,y){
  n=length(x)
  ssxx=sum((x-mean(x))^2 )
  ssxy=sum((x-mean(x))*(y-mean(y)))
  b1hat=ssxy/ssxx
  b0hat=mean(y)-b1hat*mean(x)
  yhat=b0hat+b1hat*x
  ssr=sum((y-yhat)^2)
  sq= ssr/(n-2)
  return(list(b1hat = b1hat, b0hat = b0hat, ssr=ssr,sq=sq, yhat=yhat))
}
x=1:20
set.seed(29);y=4+6*x + rnorm(20,0,5)
line = mysq(x=x,y=y)
line$sq
```

##How Close?

```{r}
line$sq - var(slr$residuals)
```
The estimated varience of errors is 1.501812.

##Carbon

```{r}
carb = read.csv("CARBON.csv")
line = mysq(carb$LabFurnace, carb$PilotPlant)
plot(carb$PilotPlant~carb$LabFurnace, ylab = "Pilot Test", xlab = "Lab Furnace", main = "CARBON")
abline(line$b0hat, line$b1hat, lwd = 2, col = "Blue")
```

###Residual Sum of Squares

```{r}
line$ssr
```
According to the function, the sum of squares is 4.694591.

###Estimated Variance of the Residuals

```{r}
line$sq
```
The Estimated Variance of the Residuals is 0.2041127.

###Estimated Standard Deviation of Residuals

```{r}
sqrt(line$sq)
```
The Estimated Standard Deviation of Residuals is 0.4517883.