---
title: "Lab1-R"
author: "Clayton Glenn"
date: "January 18, 2018"
output:
  pdf_document: default
  word_document:
    toc: yes
  html_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 5
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Tasks

## Task 1

### Get Working Directory
```{r task1 getwd}
getwd()
```



## Task 2

### Read DDT into Data Frame Object
```{r task2 read}
ddt <- read.csv("DDT.csv", header = TRUE)
head(ddt)
```



## Task 3

### What are the qualitative variables in "ddt"?
#### River and Species
### What are the quantitative variables in "ddt"?
#### Mile, Length, Weight, and DDT
### How many SPECIES are in the ddt data set?
#### 3 Species


### Subset of DDT With Large Mouth Bass and Weight > 800
```{r task3 subset lmb & w}
lmb800 <- subset(ddt, (SPECIES=="LMBASS" & WEIGHT > 800))
show(lmb800)
```


### Subset of DDT With SCM and DDT > 4.0
```{r task3 subset scm & ddt}
scmddt <- subset(ddt, (RIVER=="SCM" & DDT > 4.0))
show(scmddt)
```



## Task 4

### Table of Rivers
```{r task4 table rivers}
rT <- with(ddt, table(RIVER))
show(rT)
```


### Barplot of Rivers
```{r task4 river barplot}
rB <- barplot(rT, beside=TRUE, col=1:4)
show(rB)
```


### Table of Rivers Crossed With Species
```{r task4 river cross species}
rsT <- with(ddt, table(RIVER, SPECIES))
show(rsT)
```


### Barplot of Rivers Crossed With Species
```{r task4 river cross species barplot}
rcsB <- barplot(rsT, beside=TRUE, col=1:4)
show(rcsB)
```



## Task 5

### PieCharts of Species and Rivers
```{r species river piecharts}
sT <- with(ddt, table(SPECIES))
layout(matrix(c(1, 2),nr=1,nc=2))
pie(sT)
pie(rT)
```



## Task 6

### BoxPlots of DDT, Weight, and Length
```{r ddt, w, l boxplots}
layout(matrix(c(1,2,3),nr=1,nc=3))
with(ddt,boxplot(LENGTH,ylab="DDT",col="Blue",notch=TRUE))
with(ddt,boxplot(WEIGHT,ylab="WEIGHT",col="Green",notch=TRUE))
with(ddt,boxplot(MILE,ylab="LENGTH",col="Red",notch=TRUE))
```



## Task 7

### Coplot of Length V Weight Given River
```{r l v w give river coplot}
lwC <- coplot(LENGTH ~ WEIGHT | RIVER, ddt, col = 1:5)
```


### Coplot of DDT V Weight Given Species
```{r ddt v w give species coplot}
dwC <- coplot(DDT ~ WEIGHT | SPECIES, ddt, col = 1:4)
```




## Task 8

### ggplot Box Plot Given Species and Weight
```{r ggbox give species w}
library(ggplot2)
swgg <- ggplot(ddt, aes(x=SPECIES, y=WEIGHT, color=RIVER, fill = RIVER))
swgg <- swgg + geom_boxplot(colour = "#1F3552")
swgg <- swgg + ggtitle("Clayton Glenn")
show(swgg)
```


### Violin Plot given River and Length
```{r ggviolin give river l}
library(ggplot2)
rlgg <- ggplot(ddt, aes(x=RIVER, y=LENGTH, color=SPECIES, fill = SPECIES))
rlgg <- rlgg + geom_violin(colour = "#1F3552")
rlgg <- rlgg + ggtitle("Clayton Glenn")
show(rlgg)
```


### gg Scatter Plot given Weight and Length
```{r ggscatter give w l}
library(ggplot2)
ggplot(ddt, aes(x=WEIGHT, y=LENGTH, color=SPECIES, fill = SPECIES)) + geom_point() + ggtitle("Clayton Glenn")
```




# Clicker Questions
## Length Mean
```{r get mean}
mean(ddt$LENGTH)
```

## Weight Standard Deviation
```{r get standard deviation}
sd(ddt$LENGTH)
```
