---
title: "Lab13"
author: "Clayton Glenn"
date: "April 20, 2018"
output:
  html_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 5
    number_sections: yes
    toc: yes
  pdf_document: default
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Task 1
```{r}
getwd()
```

#Task 2
```{r}
set.seed(13); x=rnorm(40,mean=15,sd=5)
set.seed(20); y=rnorm(35,mean=10,sd=4)

x;

```
Yes, we do not have enough evidence to reject the equality ratio 1:1.


The null hypothesis would be
\[H_0=0,\ \ \ \ \  H_n\neq0\]

```{r}
t.test(x,y, mu=0,var.equal=TRUE,conf.level = .95)
```

The null hypothesis of zero is definitely rejected.
95% confidence intervals show (3.292 , 7.439).
Mu-x is extremely likely greater than Mu-y.

```{r}
set.seed(13); x=rnorm(40,mean=15,sd=5)
set.seed(20); y=rnorm(35,mean=14,sd=4)
t.test(x,y,alt="greater")
```
The P-value shows that the even though, x is greater, the data can be expressed as equal data.
The confidence intervals are (-.361 , Inf).


#Task 3
```{r}
set.seed(50); x=rnorm(30,mean=50, sd=10)
set.seed(40); y=rnorm(40,mean=55, sd=20)

var.test(x,y) #1
var.test(y,x) #2
```
The Ratios of the var.tests only differ as in the first test ratio is about 1/5 and the second test is its reciprocal. This is true since sigma1/sigma2 and the same data is flipped for both tests. The p-values are absolutely the same at .0000209. The confidence intervals are only based of F-value and since F values are reciprocals of eachother, the CI's are flipped and reciprocalled.

```{r}
var.test(x,y,alt="less")#3
var.test(y,x,alt="greater")#4
```

The F-values are reciprocals, the P-values are the same, and the CI's are reciprocals and lie inbetween (0 , Inf).


#Task 4
Something is claimed a conjugate distribution if and only If the posterior distributions are in the same probability distribution family as the prior probability distribution.

The posterior is algebraically equal to a Beta.

\[P(q|s,f)=\frac{q^{s}(1-q)^{f}}{B(s+1,f+1)}\]

Posterior hyperparameters are 5,7.

The moment estimate is 1/2.

The mean value of the posterior is 1/2.

```{r}
set.seed(19); x = rbinom(10,1,0.5)
a = qbeta(1-.95/2,shape1=1,shape2=1)
b = qbeta(.95/2,shape1=1,shape2=1)
ci=c()
ci[1]= 1-a*sqrt((.5*.5)/10)
ci[2]= 1+a*sqrt((.5*.5)/10)
ci
```