---
title: "Assignment3"
author: "Clayton Glenn"
date: "March 26, 2018"
output: 
  word_document:
    toc: yes
  pdf_document: default
  html_document:
    code_folding: show
    fig_caption: yes
    fig_height: 4
    fig_width: 5
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Assignment 3 - 10/14 Questions Complete

##Question 1

###A

\[P(y\geq 120)=e^{-120/95}\]
\[P(y\geq 120)=e^{-1.263}\]
\[P(y\geq 120)=0.283\]

###B

```{r}
p.df = read.csv("PHISHING.csv")

hist(p.df$INTTIME)
myexp = function(x, a, b) {
  (a / b) * '^'(2.71828183,-(a * x / b))
}
curve(
  myexp(x, 1, 95)*10000, #Just for sizing to actual times. Could have went other way
  xlim = c(0, 500),
  ylim = c(0, 100),
  col = "Blue",
  lwd = 2,
  ylab = "Exponential Density",
  main = "Alpha = 1, Beta = 95",
  add=TRUE
)

```

Yes, you can clearly see that the data follow an exponential distribution of B=95

##Question 2

###A

\[Mean=\mu =\alpha \beta = 3(.07) = .21\]
\[Variance = \sigma^2 =\alpha \beta^2 = 3(.07)^2=0.0147\]

###B

\[Standard\ Deviation = \sigma = \sqrt{\sigma^2}=\sqrt{0.0147}=0.1212\]
\[\mu+\sigma+\sigma = .4524\]

.60 million cubic feet lies well out of 2 standard deviations of the mean, so no, I would not expect to observe .60 in a gamma distribution with the constraints as this one. The data seems insufficient.

##Question 3

###A

\[A(\alpha=2,\beta=2)\]
\[B(\alpha=1,\beta=4)\]
\[Expected\ length\ of\ time(A) = \frac{\alpha}{\beta} = 2/2 = 1\]
\[Expected\ length\ of\ time(B) = \frac{\alpha}{\beta} = 1/4 = 0.25\]

###B

\[Variance\ length\ of\ time(A) = \frac{\alpha}{\beta^2} = 2/4 = 0.5\]
\[Variance\ length\ of\ time(B) = \frac{\alpha}{\beta^2} = 1/16 = 0.0625\]

###C

\[P(A<1)=\int^1_0 \frac{\beta^\alpha}{\Gamma(\alpha)}x^{\alpha - 1}e^{-\beta x}\]
\[P(A<1)=\int^1_0 \frac{2^2}{\Gamma(2)}x^{2 - 1}e^{-2 x}\]
\[\Gamma(2)=1\]
\[P(A<1)=4\int^1_0 xe^{-2 x}\]
\[P(A<1)=4[-\frac{xe^{-2x}}{2}-\frac{e^{-2x}}{4}|^1_0\]
\[P(A<1)=4[\frac{1}{4}-\frac{e^{-2}}{2}-\frac{e^{-2}}{4}]\]
\[P(A<1)=1-3e^{-2}\]
\[P(A<1)=.594\]

\[P(B<1)=\int^1_0 \frac{\beta^\alpha}{\Gamma(\alpha)}x^{\alpha - 1}e^{-\beta x}\]
\[P(B<1)=\int^1_0 \frac{4^1}{\Gamma(1)}x^{1 - 1}e^{-4 x}\]
\[\Gamma(1)=1\]
\[P(B<1)=4\int^1_0 e^{-4 x}\]
\[P(B<1)=-1[e^{-4x}|^1_0\]
\[P(B<1)=-[e^{-4}-e^0]\]
\[P(B<1)=1-e^{-4}\]
\[P(B<1)=.9817\]

Formula B has a higher probability of generating human reaction in less than 1 minute.

##Question 4

###A

\[F(x)=\frac{\alpha}{\beta}y^{\alpha - 1}e^{-y^{\alpha}/\beta}\]
\[P(x<2)=F(2)=\int^2_0\frac{\alpha}{\beta}y^{\alpha - 1}e^{-y^{\alpha}/\beta}dy\]
\[P(x<2)=1-e^{-2^2/4}\]
\[P(x<2)=1-e^{-1}\]
\[P(x<2)=0.63212\]

###B

\[Mean = \mu = \beta^{1/\alpha}\Gamma(\frac{\alpha+1}{\alpha})\]
\[\mu = 2\Gamma(\frac{3}{2})\]
\[\mu = 1.7316\]
\[Variance = \sigma^2 = \beta^{2/\alpha}[\Gamma(\frac{\alpha+2}{\alpha})-\Gamma^2(\frac{\alpha+1}{\alpha})]\]
\[\sigma^2 = 4[\Gamma(\frac{1}{2})-\Gamma^2(\frac{3}{2})]\]
\[\sigma^2 = 4[0.886-0.8698]\]
\[\sigma^2 = 0.93\]

###C

\[P(\mu-2\sigma < X < \mu+2\sigma) = P(-0.08 < X < 3.64)\]
\[P(-0.08 < X < 3.64) = P(x<3.64)-P(x<-0.08)\]
\[=F(3.64)-F(-0.08)\]
\[P(-0.08 < X < 3.64)=e^{0.04^4}-e^{-(1.82)^4}=0.99\]

###D

\[P(X>6)=1-F(6)=e^{-3^4}=6X10^{-36}\]

It is very unlikely that the machine will exceed 6 years without repair.

##Question 5

###A

\[Mean = \mu = \frac{\alpha}{\alpha+\beta}=2/11\]
\[Variance = \sigma^2=\frac{\alpha \beta}{(\alpha +\beta)^2(\alpha+\beta+1)}=\frac{18}{11^2(12)}=18/1452\]

###B

\[P(Y \geq 0.40) = 1 - \frac{1}{B(2,9)}\int^{0.40}_0y(1-y)^8dy\]
\[P(Y \geq 0.40) = 1 - \frac{1}{B(2,9)}([\frac{-y(1-y)^9}{9}|^{0.40}_0-[\frac{(1-y)^{10}}{90}|^{0.40}_0)\]
\[P(Y \geq 0.40) = 1 - \frac{1}{\frac{\Gamma(2) \Gamma(9)}{\Gamma(11)}}(0.0106)=.9998\]

###C

\[P(Y \leq 0.10) = \frac{1}{B(2,9)}([\frac{-y(1-y)^9}{9}|^{0.1}_0 [\frac{(1-y)^10}{90}|^{0.1}_0)\]
\[P(Y \leq 0.10) = \frac{1}{B(2,9)}(0.0029)\]

##Question 6

###A

\[f(y)=\alpha \beta y^{\beta -1}e^{-\alpha y^{\beta}}\]
\[\beta = 2,\ \alpha=1/16\]

###B

\[Mean = 1/8 \int^{\infty}_0y^2e^{-y^2/16}dy = = 2\sqrt{\pi}=3.545\]
\[E(X^2)=1/8\int^{\infty}_{0}y^3e^{-y^2/16}dy=16\]
\[Variance = E(X^2)-E(X)^2=16-4pi = 3.4335\]

###C
\[P(X \geq 6)=1-P(X < 6)=1-F(6)=1-1/8\int^{6}_{0}ye^{-y^2/16}=1-0.8946=0.1054\]

##Question 7

###A
\[P(x,y)=1/36,\ 1\leq x\leq 36,\ 1 \leq y \leq 36\]

###B

\[P_1(x)=\sum^{6}_{y=0}\frac{1}{36} = 6/36 = 1/6\]
\[P_2(y)=\sum^{6}_{y=0}\frac{1}{36} = 6/36 = 1/6\]

###C

\[P_1(x|y)=\frac{P(x,y)}{P_2(y)}=\frac{1/36}{1/6}=6/36=1/6\]
\[P_2(y|x)=\frac{P(x,y)}{P_1(x)}=\frac{1/36}{1/6}=6/36=1/6\]

###D
\[P(x,y)=P_1(x)P_2(y)\]
\[1/36=1/6*1/6\]
This shows X and Y are independent.

##Question 8

###A

P(EnergyLevel, TimePeriod)= {0.142857, 0.285714, 0.142857, 0, 0, 0.285714, 0, 0, 0.142857}

###B

\[P_1(X=1) = 0.142857\]
\[P_1(X=2) = 0.285714\]
\[P_1(X=3) = 0.571428\]

###C

\[P_2(Y=1) = 0.571428\]
\[P_2(Y=2) = 0.285714\]
\[P_2(Y=3) = 0.142857\]

###D
\[P_2(y|x)=P(Y\cap X)/P(X)\]
\[P_2(y=1|x=1)=P(Y=1\cap X=1)/0.143=1\]
\[P_2(y=2|x=1)=P(Y=2\cap X=1)/0.143=0\]
\[P_2(y=3|x=1)=P(Y=3\cap X=1)/0.143=0\]
\[P_2(y=1|x=2)=P(Y=1\cap X=2)/0.285=1\]
\[P_2(y=2|x=2)=P(Y=2\cap X=2)/0.285=0\]
\[P_2(y=3|x=2)=P(Y=3\cap X=2)/0.285=0\]
\[P_2(y=1|x=3)=P(Y=1\cap X=3)/0.571=1/3\]
\[P_2(y=2|x=3)=P(Y=2\cap X=3)/0.571=2/3\]
\[P_2(y=3|x=3)=P(Y=3\cap X=3)/0.571=1/3\]

##Question 9

###A
\[f(y)=\int^{\infty}_{-\infty}f(x,y)dx\]
\[f(y)=\int^{2y}_{y}\frac{e^{-y/10}}{10y}dx=\frac{e^{-y/10}}{10}\]
Exponential Distribution

###B

\[Mean = \mu = \beta = 10\]

##Question 10

###A

\[1=\int^\infty_0\int^x_0ce^{-x^2}dydx=\int^\infty_0[yce^{-x^2}|^x_0dx\]
\[=\int^\infty_0xce^{-x^2}dx=1/2[-ce^{-2x}|^\infty_0=\frac{c}{2}\]
\[1=C/2 \Rightarrow C=2\]

###B

\[f(x)=\int^x_0ce^{-x^2}dydx=[yce^{-x^2}|^x_0=2xe^{-x^2}=1\]
\[1/2=xe^{-x^2}\]

###C

\[f(y|x)=\frac{f(x,y)}{f(x)}=\frac{2e^{-x^2}}{2xe^{-x^2}}=1/x\]

##Question 11

##Question 12

##Question 13

##Question 14
